Clustering exploration for `r params$sample_id`

### 2024-09-13 analyses/cell-type-wilms-tumor-06/notebook_template/03_clustering_exploration.Rmd
Add notebook 03- to PR#750

    - `fetal_nephron` subtypes: podocytes, uteric bud, ...

@@

```{r fig.width=20, fig.height=15, out.width='100%'}
p1 <- do_Table_Heatmap( srat,
                            last_group = "fetal_kidney_predicted.compartment",
                            first_group = "cellassign_celltype_annotation"

@@

p1 <- do_Table_Heatmap( srat,
                            last_group = "fetal_kidney_predicted.cell_type",
                            first_group = "singler_celltype_annotation"

>>>>

    - `fetal_nephron` subtypes: podocytes, uteric bud, mesenchymal cells (that appear to be cap mesenchyme cells) ...

@@

```{r fig.width=20, fig.height=10, out.width='100%'}
p1 <- do_Table_Heatmap( srat,
                            last_group = "fetal_kidney_predicted.compartment",
                            first_group = "cellassign_celltype_annotation"

@@

p2 <- do_Table_Heatmap( srat,
                            last_group = "fetal_kidney_predicted.cell_type",
                            first_group = "singler_celltype_annotation"
